Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2023-02-17 paper/paper.tex
Add corrections to section 2

The \brfcs\ OSATE environment provides designers with workflow and tool support for developing products with
inherent cyber-resiliency.
%
\figref{fig:flowchart} is a simplified illustration of the toolkit that omits tooling outside of our contributions discussed here (see \cite{dcrypps2019,gearcase2020,resolute-destion,attestation-copland,awas,hamr,sel4-sosp09, sel4-tocs14, sel4-cacm18} for other aspects of \brfcs).
%
The shaded boxes represent our contribution: test contracts, code contracts, and SPLAT synthesis.
The unshaded boxes are the existing tools that provide the foundation for our contributions.

@@

\figref{fig:workflow} shows the intent of this behavioral contract definition of the UAV software system on the left-side of the figure at the arrow marked start.
%
The \agr\ verification engine tries to prove if the component composition of the software system is correct.
%
It is an iterative process where the designer updates contracts in the composition until \agr\ proves out the composition.
%
For our example, the initial specifications described above pass verification, meaning that the contract composition of the components with the system satisfies all component input assumptions and system output guarantees.
%
The \agr\ verification conditions, syntax and semantics, and the baseline contracts for the example are discussed in detail in \secref{sec:agree}.
%
\figref{fig:sw} in that section is the \agr\ contract for SW.

@@

\subsection{Adding cyber requirements}

Having passed \agr\ verification, the workflow in \figref{fig:workflow} proceeds to the threat analysis stage.
%
The UAV must actively protect itself from malicious actors, but to this point, the designers have only been focusing on its core functional behavior with little consideration for cyber-resilience.
%
A cyber-vulnerability analysis identifies the potential of a supply chain attack through the AI route planner since its third-party.
%
Based on the analysis, the designer adds a requirement that the system must guard against malicious AI behavior.
%
This requirement is reflected in the component contracts by removing all output guarantees from the AI contract since that component is considered untrusted.
%
Without output guarantees, the AI component is able to output arbitrary events in the \agr\ verification analysis.

The output from that analysis is shown in \figref{fig:example-certificate}.
%
The red exclamation points designate component assumptions or system output guarantees that do not hold, and each failure comes with a corresponding counter-example.
%
The first violation is that the mission command on \texttt{AutomationResponse} from the AI to the WM is no longer guaranteed to be well-formed: the red exclamation point on \emph{WM assume: Automation responses are well-formed}.
%
The consequence of that failing input assumption is that the WM outputs are no longer guaranteed.
%
For a contract, when an input assumption does not hold, then the output may be arbitrary.
%
The now arbitrary output from the WM due to input assumption violations lead to the rest of the failures in \figref{fig:example-certificate} as the WM provides the system level outputs.

@@

\subsection{Adding high assurance components}

@@

Code contracts for high assurance components can be arbitrarily complex since they can have persistent state that evolves over time.
%
Test contracts allow the designer to validate code contract behavior with unit testing.
For example, one of the test contracts for the monitor is that when it sees an automation response one step after a request, then it should not alert, and it should pass the response downstream.
%
Test contracts are discussed in detail in \secref{sec:testing}.
%
An example test from that section the the monitor in our example here is shown in \figref{fig:test}.

As shown in \figref{fig:workflow}, making the system cyber-resilient is an iterative process of adding high-assurance components, writing their code contracts, testing those contracts with test contracts, and then seeing if they are sufficient to prove out the system.
%
Having completed such an iterative for our example system, the \agr\ analysis of the cyber-hardened implementation is shown in \figref{fig:hardened-certificate}.
%
\figref{fig:hardened-certificate}(a) is the test contract results and \figref{fig:hardened-certificate}(b) is the hardened system composition.
%
Here \agr\ has generated high-level evidence justifying the claim that the high-assurance components meet their intended purposes.
%
Having passed \agr\ verification, the high-assurance components are ready to be synthesized.

@@

As \agr\ now proves the system now meets its cyber-requirements, the workflow moves to the right in \figref{fig:workflow} to the code generation box.
%
High-assurance components are automatically synthesized by \splt\ from the code contracts to equivalent programs in the \ckml\ language.
%
In other words, for any set of input streams that meet the component's contract assumptions, the output streams produced from the synthesized \ckml\ code exactly match those defined by the contract guarantees.

>>>>

The \brfcs\ OSATE environment provides designers with workflow and tool support for developing products with
inherent cyber-resiliency.
%
\figref{fig:flowchart} is a simplified illustration of the toolkit that omits tooling outside of our contributions discussed here (see \cite{dcrypps2019,gearcase2020,resolute-destion,attestation-copland,awas,hamr,sel4-sosp09, sel4-tocs14, sel4-cacm18} for other aspects of \brfcs).
%
The shaded boxes represent our contribution: test contracts, code contracts, and SPLAT synthesis.
The unshaded boxes are the existing elements that provide the foundation for our contributions.

@@

This behavioral contract definition of the UAV software system is the starting point on the left-side of \figref{fig:workflow}.
%
The \agr\ verification engine tries to prove if the component composition of the software system is correct.
%
It is an iterative process where the designer updates contracts in the composition until \agr\ proves out the composition.
%
For our example, the initial specifications described above pass verification, meaning that the contract composition of the components with the system satisfies all component input assumptions and system output guarantees.
%
The \agr\ verification conditions, syntax and semantics, and the baseline contracts for the example are discussed in detail in \secref{sec:agree}.
%
\figref{fig:sw} in that section is the \agr\ contract for SW.

@@

\subsection{Adding Cyber Requirements}

Having passed \agr\ verification, the workflow in \figref{fig:workflow} proceeds to the thread analysis as the UAV must actively protect itself from malicious actors.
%
Threat analysis identifies the potential of a supply chain attack through the AI route planner since its third-party.
%
To mitigate the identified supply chain attack, the designer adds a requirement that the system must guard against malicious AI behavior.
%
This requirement is reflected in the component contracts by removing all output guarantees from the AI contract since that component is considered untrusted.
%
Without output guarantees, the AI component is able to output arbitrary events in the \agr\ verification analysis.

The output from that analysis is shown in \figref{fig:example-certificate}.
%
The red exclamation points designate component assumptions or system output guarantees that do not hold, and each failure comes with a corresponding counter-example.
%
The first violation is that the mission command on \texttt{AutomationResponse} from the AI to the WM is no longer guaranteed to be well-formed: the red exclamation point on \emph{WM assume: Automation responses are well-formed}.
%
The consequence of that failing input assumption is that the WM outputs are no longer guaranteed.
%
For a contract, when an input assumption does not hold, then the output may be arbitrary.
%
The rest of the failures in \figref{fig:example-certificate} are the result of the WM outputs now being arbitrary.

@@

\subsection{Adding High-assurance Components}

@@

Code contracts for high assurance components can be arbitrarily complex since they can have persistent state that evolves over time.
%
Test contracts allow the designer to validate code contract behavior with unit testing.
For example, one of the test contracts for the monitor is that when it sees an automation response one step after a request, then it should not alert, and it should pass the response downstream.
%
Test contracts are discussed in detail in \secref{sec:testing}.
%
\figref{fig:test} in that section is an example test contract for the added monitor in our example.

As shown in \figref{fig:workflow}, making the system cyber-resilient is an iterative process of adding high-assurance components, writing their code contracts, testing those contracts with test contracts, and then seeing if they are sufficient to prove out the system.
%
The \agr\ analysis of the cyber-hardened implementation at the end of that iterative process is shown in \figref{fig:hardened-certificate}.
%
\figref{fig:hardened-certificate}(a) is the test contract results and \figref{fig:hardened-certificate}(b) is the hardened system composition.
%
Here \agr\ has generated high-level evidence justifying the claim that the high-assurance components meet their intended purposes.

@@

As \agr\ proves the system now meets its cyber-requirements, the workflow moves to the right in \figref{fig:workflow} to the code generation box.
%
High-assurance components are automatically synthesized by \splt\ from the code contracts to equivalent programs in the \ckml\ language.
%
In other words, for any set of input streams that meet the component's contract assumptions, the output streams produced from the synthesized \ckml\ code exactly match those defined by the contract guarantees.
